Race to the Ballot Box: Will Demographics Decide a Winner This Year?

### 2024-10-30 paper/paper.qmd
Adding the results table to the paper

>>>>

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(rstanarm)
library(caret)
library(kableExtra)
library(arrow)

electoral_votes <- data.frame(
  state = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", 
            "Connecticut", "Delaware", "District of Columbia", "Florida", "Georgia", 
            "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", 
            "Louisiana", "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota",
            "Mississippi", "Missouri", "Montana", "Nebraska", "Nevada", 
            "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", 
            "North Dakota", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", 
            "Rhode Island", "South Carolina", "South Dakota", "Tennessee", "Texas", 
            "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", 
            "Wyoming"),
  votes = c(9, 3, 11, 6, 54, 10, 7, 3, 3, 30, 16, 4, 4, 19, 11, 6, 6, 8, 8, 4, 10, 11, 
            15, 10, 6, 10, 4, 5, 6, 4, 14, 5, 28, 16, 3, 17, 7, 8, 19, 4, 9, 3, 11, 
            40, 6, 3, 13, 12, 4, 10, 3)
)

set.seed(12)
data <- read_parquet("../data/analysis_data/analysis_data.parquet")
model <- readRDS("../models/election_model.rds")
training_index <- createDataPartition(data$candidate_trump, p = 0.7, list = FALSE)
testing_data <- data[-training_index,]

testing_data |>
  select(pollster, state, candidate_trump, pct) |>
  mutate(
    state = recode(state, "Maine CD-1" = "Maine", 
                          "Maine CD-2" = "Maine",
                          "Nebraska CD-2" = "Nebraska"),
    predicted_pct = 100 * posterior_predict(model, newdata = testing_data, 
                                                  draws = 2000, type = "response") |> colMeans(),
    winner_trump = ifelse(predicted_pct > 50, 1, 0)
  ) |>
  group_by(state) |> 
  summarise(predicted_prob = round(mean(predicted_pct), 2), .groups = "drop") |>
  left_join(electoral_votes, by = c("state" = "state")) |>
  mutate(predicted_winner = ifelse(predicted_prob > 50, "Trump", "Harris")) |>
  kbl(booktabs = TRUE, col.names = c("State", "Predicted Trump %", "Electoral Votes", "Predicted Winner"))
```
